---
title: "3D Scans In Plotly With R"
author: "Peter Dunham"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plotly 3D Surface Plot

The following surface plot was created with Plotly in R. The raw data was collected with a scanner on a motion platform similar to a 3D scanner. The item being shown is a portion of a semiconductor wafer holder ("a chuck").  

```{r echo=FALSE, warning=FALSE, message=FALSE}
  library(dplyr)
  library(akima)
  library(plotly)
  
  data<-read.csv("Chuck.txt")
  names(data)<-c("location","xpos","ypos","ain")
  data$ain<-data$ain*-1
  
  x<-data$xpos
  y<-data$ypos
  z<-data$ain
  
  #yop and xop determine resolution of surface plot
  # these are use as interp parameters
  yop<-as.matrix(seq(-11800, 11800, 100))
  xop<-as.matrix(seq(-12000, 12000, 100))
  
  data<-data.frame(x,y,z)
  chuckToPlot <- with(data,interp(x,y,z, yo=yop, xo=xop))

  plot_ly(z=chuckToPlot$z, type="surface")
```

## Plotly 3D Surface Plot of 3D Scanned Circuit Board

The following surface plot was created with Plotly in R. The raw data was collected with a scanner on a motion platform similar to a 3D scanner. The item is a small circuit board.  

```{r echo=FALSE, warning=FALSE, message=FALSE}


  library(dplyr)
  library(akima)
  library(plotly)
  
  #Getting and scaling the data
  circuit_data<-read.csv("CircuitUniDirectionFlat.txt", header=FALSE)
  xseq<-seq(1,length(circuit_data[,1]),by=3)
  yseq<-seq(2,length(circuit_data[,1]),by=3)
  ainseq<-seq(3,length(circuit_data[,1]),by=3)
  x<-circuit_data[xseq,][1:129999]
  x<-x/50
  y<-circuit_data[yseq,][1:129999]
  y<-y/50
  z<-circuit_data[ainseq,][1:129999]
  z<-z/1
  z<-z*-1
  circuit_data<-data.frame(x,y,z)[1:127926,]
  data<-circuit_data
  

  #yop and xop determine resolution of surface plot
  # these are use as interp parameters
  xop<-as.matrix(seq(min(x), max(x), 200)) #100 here, worked well
  yop<-as.matrix(seq(min(y), max(y),200))
  
  data<-data.frame(x,y,z)
  circuitToPlot <- with(data,interp(x,y,z, yo=yop, xo=xop, duplicate="mean"))
  
  plot_ly(z=circuitToPlot$z, type="surface")%>% 
    layout(
      scene = list(
        zaxis = list(range = c(-50000,-20000)),
        aspectratio = list(x = 1, y = .3, z = .1)
      )
    )
  


```
