---
title: "Plotly Presentation"
author: "Peter Dunham"
date: "March 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plotly 3D Surface Plot

The following surface plot was created with Plotly in R. The raw data was collected with a scanner on a motion platform similar to a 3D scanner. The item being shown is a portion of a semiconductor wafer holder ("a chuck").  Because of the amount of data, it may take some time to load, but is responsive after initial loading.  I found this plotly renders fine in Chrome and MS Edge, it currently does not appear to load in Firefox.

```{r echo=FALSE, warning=FALSE, message=FALSE}
  library(dplyr)
  library(akima)
  library(plotly)
  
  data<-read.csv("Chuck.txt")
  names(data)<-c("location","xpos","ypos","ain")
  data$ain<-data$ain*-1
  
  x<-data$xpos
  y<-data$ypos
  z<-data$ain
  
  #yop and xop determine resolution of surface plot
  # these are use as interp parameters
  yop<-as.matrix(seq(-11800, 11800, 100))
  xop<-as.matrix(seq(-12000, 12000, 100))
  
  data<-data.frame(x,y,z)
  chuckToPlot <- with(data,interp(x,y,z, yo=yop, xo=xop))
  #with(chuckToPlot,image(x,y,z))
  plot_ly(z=chuckToPlot$z, type="surface")
```


